Optimal (Multiway) Spatial Joins

### 2024-05-29 msj.tex
yufei

Fix any rectangle $r \in R_1 \cup ... \cup R_{k-2}$ and any vertical segment $v$ from $V$ that crosses $r$. An argument symmetric to the above shows that $v$ must also cross $r'$.

@@

\vgap 
\input{4.2.tex}

>>>>

Fix any rectangle $r \in R_1 \cup ... \cup R_{k-2}$ and any vertical segment $v$ from $V$ that crosses $r$. An argument symmetric to the above shows that $v$ must also cross the trimmed rectangle $r'$.

@@

\noindent \underline{\em Proof of Statement (3).} Consider an arbitrary $\bm{t} \in \J(R_1',...,R_{k-2}')$. First, we claim that $|\dcross_H(\bm{t})| \neq \emptyset$. Let $r' = \gbot(\bm{t})$, and let $r$ be the full rectangle of $r'$. Let $h$ be the lowest segment that crosses $r$. We will prove the claim by showing that $h \in \dcross_H(\bm{t})$. More specifically, we will prove that $h$ crosses $B_{\bm{t}}$ and $r'$. From the first paragraph of the proof of Statement (2), we know that $h$ crosses $r'$ because $h$ crosses $r$.
By how $r'$ is defined, the bottom edge of $r'$ is contained in $h$. Since $r' = \gbot(\bm{t})$, the bottom edge of $B_\bm{t}$ is contained in the bottom edge of $r'$, and hence in $h$. Thus, $h \cap B_{\bm{t}}\neq \emptyset$. Since $h$ crosses $r'$, $r'$ does not contain any of the endpoints of $h$. As $r'$ covers $B_{\bm{t}}$, $B_{\bm{t}}$ does not contain any of the endpoints of $h$. Thus, $h$ crosses $B_{\bm{t}}$. This proves that $h \in \dcross_H(\bm{t})$, and hence $|\dcross_H(\bm{t})| \neq \emptyset$. By symmetry, $|\dcross_V(\bm{t})|$ is also nonempty. Equivalently, we have $|\dcross_H(\bm{t})| \geq 1$ and $|\dcross_V(\bm{t})| \geq 1$.

Therefore, to prove Statement (3),
it suffices to show that \\
\myeqn{
    \sum_{\bm{t}\in \J(R_1',...,R_{k-2}')}(|\dcross_H(\bm{t})|\cdot |\dcross_V(\bm{t})|) \leq \out. \label{eqn:lmm4.2.3}
    } Recall that $\J^*$ is the set of tuples generated by the algorithm \textbf{generate-$\J^*$}(see below Example 4.3). By the discussion following the algorithm, we have $\J^*\subseteq \J(R_1,...,R_{k-2},H,V)$, which means $|\J^*|\leq \out$. Thus, we can prove Inequality~\eqref{eqn:lmm4.2.3} by showing that its left-hand side is equal to $|\J^*|$.
 By the line 2-4 of \textbf{generate-$\J^*$}, the number of tuples generated in line 5 is exactly the left-hand side of Inequality~\eqref{eqn:lmm4.2.3}.
Besides, it is obvious that every tuple $(r_1,...,r_{k-2},h,v)$ generated in line 5 of \textbf{generate-$\J^*$} is unique. Therefore, Inequality~\eqref{eqn:lmm4.2.3} holds. This completes the proof of Statement (3).
